---
title: "Face and Object Recognition"
author: "Melisa Holdway and Brandy Bishop"
date: "May 28, 2016"
output: html_document
---
The first thing we have to do is read the data.
```{r}
dat=read.csv("data.csv")
```
Next, we check the structure.
```{r}
str(dat)
```
From the structure we can see that Participants is an integer and we want is as a factor.
```{r}
dat$Participant<-as.factor(dat$Participant)
```
Now that we have changed Participants to a factor, lets check the mean and standard of the face and object conditions
```{r}
mean(dat$Scores[dat$Condition=="Face"])
mean(dat$Scores[dat$Condition=="Object"])
sd(dat$Scores[dat$Condition=="Face"])
sd(dat$Scores[dat$Condition=="Object"])
```
These results show that the mean correct score for the face condition was 7.57, with a standard deviation of 1.4, while the object condition had a mean correct score of 6.89 and a standard deviation of 1.49. 
Now, lets run our ANOVA.
```{r}
summary(aov(Scores~Condition+Error(Participant/Condition),data=dat))
```
From this, we can see that Condition had a significant effect F(1,34) = 4.39, p.< .05. 
In order to make sure that we do not reject the null hypothesis in error, we will now run a t-test.
```{r}
t.test(dat$Scores[dat$"Condition"=="Face"],dat$Scores[dat$"Condition"=="Object"],var.equal=TRUE,paired=TRUE)
```
This shows that t(34) = 2.09, p. < .05 which confirms that the correct scores for faces is signifantly higher than the correct scores for objects, thus confirming the null hypothesis. 

Lastly, we will graph our results using a bar graph. 
```{r}
library(ggplot2)
library(gplots)
library(dplyr)
```
```{r}
temp<-dat%>%group_by(Condition)%>%summarize(means=mean(Scores),
sems=sd(Scores)/sqrt(length(Scores)))
f<-ggplot(temp,aes(x=factor(Condition),y=means))+
geom_bar(stat="identity", color="black",
fill=c("blue", "red"))+
geom_errorbar(aes(ymax=means+sems,
ymin=means-sems),
width=.2)+
ggtitle("Recognition Rates")+
labs(x="Recognition Tasks",y="Mean Correct Responses")+
scale_x_discrete(breaks=c("Face", "Object"),
labels=c("Face", "Object"))+
theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
theme(axis.title.y=element_text(size=12,face="bold",vjust=.25))+
theme(axis.text.x=element_text(size=10,face="bold",
color="black"))+
theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
max(temp$means)+2*max(temp$sems)))+
theme(panel.border=element_blank(),axis.line=element_line())+
theme(panel.grid.major.x=element_blank())+
theme(panel.grid.major.y=element_line(color="darkgrey"))+
theme(panel.grid.minor.y=element_blank())
f
```
